Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-27 manuscript/manuscript.tex
cite fig.1 (#137)
mentioning+citing matplotlib (#137)

The underlying software stack for running the tutorial consists of:
\begin{itemize}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter notebook tool used for running the tutorials~\cite{jupyter}, along with extension packages jupyter\_contrib\_nbextensions and nbexamples
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nglview}
\end{itemize}

@@

In short, the workflow for a full analysis of an MD dataset might consist of,
\begin{itemize}
	\item extracting molecular features from the raw data (01),
	\item transforming those features into a suitable, low dimensional subspace (02),
	\item discretizing the low dimensional subsets into a state decomposition (02),
	\item estimating a maximum likelihood or Bayesian MSM from the discrete trajectories and performing validation tests (03),
	\item analyzing the stationary and kinetic properties of the MSM (04),
	\item finding metastable macrostates and applying transition path theory (TPT) to identify the pathways of conformational change (05),
	\item computing expectation values for experimental observables (06), and
	\item coarse-graining the MSM using a hidden Markov model approach (07).
\end{itemize}

>>>>

The underlying software stack for running the tutorial consists of:
\begin{itemize}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter~\cite{jupyter} notebook tool used for running the tutorials, along with extension packages jupyter\_contrib\_nbextensions and nbexamples
\item matplotlib -- A plotting library~\cite{matplotlib}
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nglview}
\end{itemize}

@@

In short, the workflow (Fig.~\ref{fig:workflowchart}) for a full analysis of an MD dataset might consist of,
\begin{itemize}
	\item extracting molecular features from the raw data (01),
	\item transforming those features into a suitable, low dimensional subspace (02),
	\item discretizing the low dimensional subsets into a state decomposition (02),
	\item estimating a maximum likelihood or Bayesian MSM from the discrete trajectories and performing validation tests (03),
	\item analyzing the stationary and kinetic properties of the MSM (04),
	\item finding metastable macrostates and applying transition path theory (TPT) to identify the pathways of conformational change (05),
	\item computing expectation values for experimental observables (06), and
	\item coarse-graining the MSM using a hidden Markov model approach (07).
\end{itemize}
